A Survey of Quantitative Descriptions of Molecular Structure

### 2012-07-05 paper.tex
Added LICSS

In addition to libraries and their wrappers there are various GUI
applications that allow easy descriptor calculations. Examples include
Bioclipse \cite{Spjuth:2007aa} (see Figure~\ref{fig:tools}), MOE (Chemical Computing Group) and
Maestro (Schr\"{o}dinger, Inc.). Workflow tools are also a useful
class of applications for descriptor generation and allow one to
easily generate descriptors from multiple sources~\cite{Truszkowski2011} (see Figure~\ref{fig:tools}). Given the focus of
this article on Open Source implementations, we have noted the
availability in Table \ref{tab:impl}. While a number of
implementations are not strictly Open Source according to OSI
definitions, the fact that they provide free academic licenses does
allow them to be used somewhat freely.

@@

\ctable[caption={Three tools to calculate descriptors: Bioclipse (top left), which allows selecting descriptor
implementations from various independent tools, CDK-Taverna (top right), which is an extension to Taverna
to calculate descriptors with the CDK, Ambit2 (bottom), which implements the OpenTox API providing
a REST-based API for descriptor calculation and wraps various descriptor calculation
tools.},cap={},label={fig:tools},botcap,figure]
{c}
{}
{
  \includegraphics[width=0.48\linewidth]{bioclipse}
  \includegraphics[width=0.48\linewidth]{cdktaverna} \\
  \includegraphics[width=0.48\linewidth]{ambitOnline}
}

>>>>

In addition to libraries and their wrappers there are various GUI
applications that allow easy descriptor calculations. Examples include
Bioclipse \cite{Spjuth:2007aa} (see Figure~\ref{fig:tools}), MOE (Chemical Computing Group) and
Maestro (Schr\"{o}dinger, Inc.) as standalone tools, but also
as a plugin to Microsoft Excel, called LICSS~\cite{Lawson2011}.
Workflow tools are also a useful
class of applications for descriptor generation and allow one to
easily generate descriptors from multiple sources~\cite{Truszkowski2011}
(see Figure~\ref{fig:tools}). Given the focus of
this article on Open Source implementations, we have noted the
availability in Table \ref{tab:impl}. While a number of
implementations are not strictly Open Source according to OSI
definitions, the fact that they provide free academic licenses does
allow them to be used somewhat freely.

@@

\ctable[caption={Four tools to calculate descriptors: Bioclipse (top left), which allows selecting descriptor
implementations from various independent tools, CDK-Taverna (top right), which is an extension to Taverna
to calculate descriptors with the CDK, Ambit2 (bottom left), which implements the OpenTox API providing
a REST-based API for descriptor calculation and wraps various descriptor calculation
tools. The bottom right screenshot shows the Microsoft Excel plugin LICSS
that uses the CDK for 2D diagrams and descriptor calculation. This screenshot is provided by Kevin
Lawson, Syngenta, UK, and reproduced with permission.},cap={},label={fig:tools},botcap,figure]
{c}
{}
{
  \includegraphics[width=0.48\linewidth]{bioclipse}
  \includegraphics[width=0.48\linewidth]{cdktaverna} \\
  \includegraphics[width=0.48\linewidth]{ambitOnline}
  \includegraphics[width=0.48\linewidth]{DescriptorTest}
}
